Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-17 manuscript.Rmd

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: html_document
header-includes:
- \usepackage{indentfirst}
- \usepackage{setspace}
- \doublespacing
- \setlength{\parindent}{4em}
---

@@

@@

```{r objectMakerProQuest, warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
# Clear workspace
rm(list=ls())

library(BibWrangleR)

# Set the path where original raw data are stored
setwd("/Users/beperron/Git/SocialWorkResearch/Data")

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data/ProQuest"

# Wrangle the data with the BWR function suite

proQuestBWR.f(csv=FALSE, path=path)
save(proQuestBWR.df, file = "ProQuest.R")
```

```{r objectMakerEbscoHost,warning=FALSE, message=FALSE, eval=FALSE, results='hide', cache=TRUE}
# Clear workspace
rm(list=ls())

# Set the path where original raw data are stored
setwd("/Users/beperron/Git/SocialWorkResearch/Data")

# Set the working directory to store files created by BWR functions
path <- "/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL"

# Wrangle the data with the BWR function suite

ebscoBWR.f(csv=FALSE, path=path)
save(ebscoBWR.df, file = "ebscoFULL.R")
```

```{r BEPinitialization, eval=TRUE}
rm(list=ls())

#load("/Users/beperron/Git/SocialWorkResearch/socialWorkHistory.Rdata")

#Load required packages
library(ggplot2)
library(dplyr)
library(gridExtra)
```

```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE, cache=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)

source("/Users/beperron/Git/SocialWorkResearch/functions/combineData.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/cleaningJournals.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/shortArticlesRevised.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/titleMatching.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/otherDocuments.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/requireAuthorJournalTitleYear.R")
source("/Users/beperron/Git/SocialWorkResearch/functions/pretty.R")

combineData.f()
cleaningJournals.f()
shortArticles.f()
titleMatching.f()
otherDocuments.f()
requireAuthorJournalTitleYear.f()
#save.image(file = "socialWorkHistory.Rdata")
```

```{r summarySetUp, eval=TRUE, cache=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r Figure 1a - Journals, cache=TRUE}
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

@@

```{r Figure 1b - Journals}
curr <- n.journals.year$Journal.count[-1]
prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
annualChange.df$year <- c(1989:2013)

@@

```{r plot02_SmallMultiples, cache=TRUE}
# Remove 2014 & 2015

@@

```{r plot03_AuthorPages, eval=TRUE, cache=FALSE}

@@

#----------------------------
#Pages
#----------------------------

@@

```{r CAGR comparison}

@@

```{r appendix_A_intersection}
unique.swHistory <- filter(full.df, attributes == "journal") %>%
    distinct(record)

@@

```{r finalArticleListecho=FALSE, comment=NA}
#print.data.frame(final.list, row.names=FALSE)
```

@@

```{r}
#plotIndex
```

```{r}
grid.arrange(plot.journal.count, plot.article.count, ncol=2)

```
\newpage
```{r fig.height=10, fig.width=7.5}
plotSmallMultiples.1

@@

\newpage
```{r fig.height=10, fig.width=7.5}
plotSmallMultiples.2

@@

```{r}

@@

```{r}
evidence.plot
```
\newpage

```{r}
stacked.plot
```

\newpage
```{r}
grid.arrange(journal.evidence.plot, propPlot, 
        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
```

@@

```{r appendix_Print, eval=TRUE}
print(sort(hodge.swHistory.diff))
print(fewArticles)
```

>>>>

---
title: 'Examining a Quarter Century of Publishing Trends in Social Work Research:
  A Data Science Perspective'
author: ''
date: "May 26, 2015"
output: html_document
---

@@

```{r LoadDatabase}
rm(list=ls())
load("HistoricalDatabase.R")

head(full.df)
dim(full.df)
```

@@

```{r summarySetUp, eval=FALSE, cache=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r Figure 1a - Journals, cache=TRUE, eval=FALSE}
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

@@

```{r Figure 1b - Journals, eval=FALSE}
curr <- n.journals.year$Journal.count[-1]
prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
annualChange.df$year <- c(1989:2013)

@@

```{r plot02_SmallMultiples, eval=FALSE}
# Remove 2014 & 2015

@@

```{r plot03_AuthorPages, eval=FALSE, cache=FALSE}

@@

```{r eval=FALSE}
#----------------------------
#Pages
#----------------------------

@@

```{r CAGR comparison, eval=FALSE}

@@

```{r appendix_A_intersection, eval=FALSE}
unique.swHistory <- filter(full.df, attributes == "journal") %>%
    distinct(record)

@@

```{r finalArticleListecho=FALSE, comment=NA, eval=FALSE}
#print.data.frame(final.list, row.names=FALSE)
```

@@

```{r, eval=FALSE}
grid.arrange(plot.journal.count, plot.article.count, ncol=2)

```
\newpage
```{r fig.height=10, fig.width=7.5, eval=FALSE}
plotSmallMultiples.1

@@

\newpage
```{r fig.height=10, fig.width=7.5, eval=FALSE}
plotSmallMultiples.2

@@

```{r eval=FALSE}

@@

```{r eval=FALSE}
evidence.plot
```
\newpage

```{r eval=FALSE}
stacked.plot
```

\newpage
```{r eval=FALSE}
grid.arrange(journal.evidence.plot, propPlot, 
        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
```

@@

```{r appendix_Print, eval=FALSE}
print(sort(hodge.swHistory.diff))
print(fewArticles)
```
